Global phase diagram and possible quantum spin liquid in the triangular $J$-$K$-$\Gamma$ model

### 2020-08-12 paper/paper.tex
20200812 9:10

Geometric frustration, which arises when the lattice geometry gives rise to constraints that not every exchange bond can be simultaneously minimized in energy, plays an important role in various kinds of magnetic systems. The nearest-neighbor (NN) antiferromagetic (AFM) Heisenberg model on the triangular lattice is a typical example, once two of the spins on an elementary triangle are antiparallel to satisfy their antiferromagnetic interaction, the third one can no longer point in a direction opposite to both other spins. In particular, the special case where spins are $S=1/2$ has attracted numerous interests and was extensively studied after the seminal prediction by Anderson of a ``quantum spin liquid" (QSL) where a strong quantum fluctuation prevents any long-range order down to the zero temperature~\cite{Anderson1973}, although it has been shown by later studies that the ground state (GS) have a classical magnetic order with each spin on a triangle pointing to 120$^\circ$ with respect to each other~\cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}. When the second NN interactions are included which introduce further frustration, the system has a much richer phase diagram including the 120$^\circ$ N\'{e}el state, the stripe state and a QSL state~\cite{PhysRevB.91.014426,PhysRevB.92.041105,PhysRevB.92.140403,PhysRevB.96.165141,PhysRevB.93.144411,JPSJ.83.093707,PhysRevB.96.075116,PhysRevB.94.121111,PhysRevLett.123.207203}. All these studies have revealed that geometric frustated systems show quite different behavior from that of the non-frustated system.

@@

In fact, magnetic ions located at the center of edge-shared octahedra can not only form the honeycomb lattice but also the triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a)), so the Kitaev and $\Gamma$ terms can naturally be generalized to the triangular lattice~\cite{PhysRevB.89.014414,PhysRevB.93.104417}. The HK model ($\Gamma=0$) on the triangular lattice has been studied by means of Luttinger-Tisza minimization together with classical Monte Carlo simulation~\cite{PhysRevB.93.104417}, exact diagonalization (ED)~\cite{KaiLi2015}, and density matrix renormalization group~\cite{JPSJ.85.114710,PhysRevX.9.021017}. All these methods give consistent results about four magnetically ordered phases: two collinear patterns of FM and stripe types, and two noncollinear patterns of 120$^\circ$ N\'{e}el and noncoplanar spiral types. Note that the distortions of the 120$^\circ$ N\'{e}el order, when the model deviates from the AFM Heisenberg limit ($K=0$, $J>0$), were also called the $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417,JPSJ.85.114710}. However, the nature of the phase around the antiferromagnetic Kitaev point is still under debate. The Luttinger-Tisza minimization method suggested it to be a $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417}, the Schwinger-fermion mean-field theory proposed it to be a QSL~\cite{KaiLi2015}, while the density matrix renormalization group calculations suggested it to be a nematic phase~\cite{JPSJ.85.114710} or a stripe phase~\cite{PhysRevX.9.021017}. When the symmetric off-diagonal exchange interaction $\Gamma$ is included, a classical analysis reveals that the stripe and ferromagnetic phases dominate the $J$-$K$-$\Gamma$ phase diagram, in addition to small regions of 120$^\circ$, $Z_{2}$ vortex crystal and nematic phases~\cite{PhysRevB.92.165108}. However, the studies on the effects of quantum fluctuations on the global $J$-$K$-$\Gamma$ phase diagram are scarce. In particular, since no exact solution has been reported so far for the pure spin-$1/2$ Kitaev and $\Gamma$ models on the triangular lattice, it also remains conceptually interesting to investigate whether QSL states could exist as possible GSs due to quantum fluctuations introduced by these exchange-frustrated interactions.

\begin{figure}
    \centering
    \begin{minipage}{0.6\columnwidth}
        \includegraphics[width=\linewidth]{fig/EdgeSharingOctahedrons.pdf}
    \end{minipage}\hspace{0pt}
    \begin{minipage}{0.3\columnwidth}
        \includegraphics[width=\linewidth]{fig/SingleOctahedron.pdf}\vspace{0pt}
        \includegraphics[width=\linewidth]{fig/ModelDefinition.pdf}
    \end{minipage}
    \caption{\label{fig:ModelDefinition}(Color online) (a) Top view of the triangular lattice of the edge-sharing octahedron. (b) The orientation of the cubic $x$, $y$, $z$ axes with respect to the octahedron. The spin operators $S^x$, $S^y$ and $S^z$ are defined with respect to this reference frame. (c) Three types of the NN bonds on the triangular lattice, namely $\gamma=x, y, z$ colored red, green and blue, respectively. The different colors of the lattice sites label the four sublattices realizing the four-sublattice-transformation, see the main text for detailed information.}
\end{figure}

On the experimental side, studies of several classes of rare-earth compounds have recently shown that the quantum spin model on the triangular lattice can be formed by $4f$ moments. In particular, due to their possible Kramers doublets and spin-orbital coupling, the $4f$ electrons can be treated as $S_{eff}=1/2$ at low temperatures, and the spin-orbit entanglement can induce direction-dependent exchanges, such as the $K$ and $\Gamma$ terms. A typical example is YbMgGaO$_{4}$~\cite{srep16419,PhysRevLett.115.167203,PhysRevLett.117.097201,nphys3971,Nature20614,PhysRevLett.117.267202,PhysRevLett.120.087201,PhysRevLett.122.137201,LiAdroja-398}, in which the Yb$^{3+}$ ions form a triangular layer and are surrounded by O$^{2-}$ which construct edge sharing octahedra~\cite{srep16419,PhysRevLett.115.167203}. At low temperatures, QSL states have been proposed due to its lack of long-range magnetic order and the observation of a continuum of magnetic excitations~\cite{srep16419,PhysRevLett.115.167203,PhysRevLett.117.097201,nphys3971,Nature20614}, but the exchange disorder induced by the intermixture of Mg$^{2+}$ and Ga$^{3+}$ may lead to a spin glass state~\cite{PhysRevLett.120.087201} or a random valence bond state~\cite{PhysRevLett.122.137201,LiAdroja-398}. More recently, an alternative family of compounds AReCh$_2$ (A=alkali, Re=rare-earth, Ch=O, S, Se) with perfect triangular lattices of rare-earth ions have been synthesized and explored. The magnetic susceptibilty and heat capacity data suggest no long-range magnetic order or spin freezing down to the lowest measurement temperature, which implies their candidacy for QSL state~\cite{acsmaterialslett.9b00464,PhysRevMaterials.3.114413,PhysRevB.100.241116,Liu_2018,PhysRevB.99.180401,PhysRevB.100.224417,PhysRevB.100.144432}. These triangluar magnets of rare-earth ions provide suitable platforms to study the interplay of geometric frustation and exchange frustration induced by spin-orbit coupling.

In this paper, we study the global phase diagram and the phase transitions of the triangular-lattice $J$-$K$-$\Gamma$ model using a combination of ED and classical analyses. We find that the ED results are basically consistent with the classical analyses such as the classical Monte Carlo simulations. In the HK limit ($\Gamma=0$), there are five classical phases: one FM, two stripe, one $120^{\circ}$ N\'{e}el and its dual phases. For the pure AFM Kitaev model, although the system has highly degenerate classical GSs composed of the stripe and nematic states, the order-by-disorder mechanism caused by quantum fluctuations makes the system select the stripe state to be the GS. When the $\Gamma$ term is included, we find five new phases: two FM, one stripe, one modulated stripe and one possible QSL phases. With the aid of classical analysis, we determine the spin directions for each magnetically ordered phase and explain that why there are phase transitions between the phases with the same type of classical orders. On the other hand, we find that the order-by-disorder mechanism makes the GSs of the pure $\Gamma$ models have FM orders, although the classical analyses suggest that the GSs are highly degenerate. For the possible QSL phase, based on the investigation of the spin excitation spectrum, we find that the GS is probably a gapped $Z_{2}$ QSL.

The rest of the paper is organized as follows: In Sec.~\ref{sec:Model} we introduce the $J$-$K$-$\Gamma$ model as well as the four-sublattice-transformation that can be applied to the HK limit. The ED and classical Monte Carlo methods are introduced in Sec.~\ref{sec:Methods}. Section~\ref{sec:Results} gives the main results of this paper.

\section{\label{sec:Model}Model}

@@

In the followings, for convenience, we fix the energy scale with $\sqrt{J^2 + K^2 + \Gamma^2}=1$ and parametrize the exchange interactions using spherical angles $\alpha$ and $\beta$
\begin{equation}
    J = \sin\alpha \sin\beta, \quad
    K = \sin\alpha \cos\beta, \quad
    \Gamma = \cos\alpha
    \label{eq:Parameters}
\end{equation}
where $\alpha \in [0, \pi]$ and $\beta \in [0, 2\pi]$ to cover the global parameter space.

In the HK limit ($\Gamma=0$), the model~\eqref{eq:Hamiltonian} admits an exact duality transformation, i.e., the so-called four-sublattice-transformation (FST)~\cite{PhysRevB.89.014414}. The FST is a spin rotation transformation which divides the triangluar lattice into four sublattices (see Fig.~\ref{fig:ModelDefinition}(c)) and performs the following rotations of the spins on the four sublattices to map the spin $\bm{S}_{i}$ to $\bm{S}_{i}^{\prime}$,
\begin{align*}
    & \bm{S}_{0}^{\prime} = \bm{S}_{0}& \quad \text{for sublattice 0}, \\
    & \bm{S}_{1}^{\prime} = (S_1^x, -S_1^y, -S_1^z)& \quad \text{for sublattice 1}, \\
    & \bm{S}_{2}^{\prime} = (-S_2^x, S_2^y, -S_2^z)& \quad \text{for sublattice 2}, \\
    & \bm{S}_{3}^{\prime} = (-S_3^x, -S_3^y, S_3^z)& \quad \text{for sublattice 3}.
\end{align*}
This corresponds to a $\pi$ rotation around $x$, $y$, and $z$ axis for the sublattices $1$, $2$, and $3$, respectively. The resulting Hamiltonian $H^{\prime}(\bm{S}^{\prime})$ has the same form as the original Hamiltonian albeit with different model parameters $J^{\prime} = -J$ and $K^{\prime} = 2J + K$. For the spherical angles defined in Eq.~\eqref{eq:Parameters}, the mapping takes the form
\begin{align}
    \tan\beta^{\prime} = -\sin\beta / (2\sin\beta + \cos\beta).
    \label{eq:FST}
\end{align}
This special property of the model can help us to identify some exotic magnetically ordered phases from the well established simple counterparts.

\section{\label{sec:Methods}Methods}

\subsection{\label{subsec:MethodED}Exact Diagonalization}

@@

To further determine the magnetic configurations of the magnetically ordered phases, we employ a method by studying the projections of the exact GSs of the finite cluster to the classical states~\cite{PhysRevB.94.064435}. The basic idea of this method is to measure the probabilities of the exact cluster GS on cluster spin coherent states with varying moment directions. The cluster spin coherent state is a direct product of spin-1/2 coherent states on each site $i$, i.e.,
\begin{align}
    | \Psi \rangle = \bigotimes_{i=1}^{N} | \theta_{i}, \phi_{i} \rangle,
    \label{eq:ClusterCoherentState}
\end{align}
where the spin-1/2 coherent state
\begin{align}
    | \theta, \phi \rangle = \mathcal{R}_{z}(\phi) \mathcal{R}_{y}(\theta) | \uparrow \rangle = e^{-i \phi S^z} e^{-i \theta S^y} | \uparrow \rangle
    \label{eq:Spin-1/2CoherentState}
\end{align}
is fully polaried state along the $(\theta, \phi)$ direction. Here the cubic axes are used (see Fig.~\ref{fig:ModelDefinition}(b)), $\theta$ and $\phi$ are the conventional spherical angles. By calculating the overlap between the exact cluster GS and cluster spin conherent states, $P = | \langle \Psi | GS \rangle |^2$, and maximizing its value with respect to $\theta$'s and $\phi$'s, we can then identify the classical spin pattern that best fits the exact quantum GS.

Since one of the key characteristics of QSL is the fractional excitation, which can lead to a continuous spectrum, so we study the dynamic structure factor (DSF) $A(\bm{k}, \omega)$ to search for the possible QSLs. $A(\bm{k}, \omega)$ is given by
\begin{align}
    & A(\bm{k}, \omega) = -\frac{1}{\pi} \text{Im} \mathcal{S}(\bm{k}, \omega), \label{eq:Akomega} \\
    & \mathcal{S}(\bm{k}, \omega) = \frac{1}{N} \sum_{ij} \mathcal{S}_{ij}(\omega) e^{i \bm{k} \cdot (\bm{R}_i - \bm{R}_j)}, \\
    & \mathcal{S}_{ij}(\omega) = \langle \Omega | S_i^{+} \frac{1}{\omega + i0^{+} - H + E_0} S_j^{-} | \Omega \rangle, \label{eq:GreenFunction}
\end{align}
where $E_0$ is the ground state energy.

\subsection{\label{subsec:MethodMC}Classical Monte Carlo}

@@

From the magnetic configuration of GS, we compute the SSF given by
\begin{align}
    \mathcal{S}_{\bm{k}} = \frac{1}{N} \sum_{ij} \left \langle \bm{S}_i \cdot \bm{S}_j \right \rangle e^{i \bm{k} \cdot (\bm{r}_i-\bm{r}_j)},
\end{align}
which is a key characterizes to identify magnetic phases.

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.95\textwidth]{fig/QuantumGlobalPhaseDiagram.pdf}
    \caption{\label{fig:QuantumPhaseDiagram}(Color online) Global phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model. The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively. There are in total ten phases including three different FM phases denoted as FM-A, FM-B and FM-C, three different stripe phases designated as Stripe-A, Stripe-B and Stripe-C, Modulated Stripe, 120$^\circ$ N\'{e}el, Dual N\'{e}el and a possible quantum spin liquid phase. The three FM phases different from each other in the direction of the ordered moment, and also the three stripe phases are distinguished by their moment directions, see main text for details.}
\end{figure*}

@@

For the other two phases with large areas and mainly located in the $J<0$ region of the phase diagram, we show the SSFs of two representative points with $\alpha=0.3\pi, \beta=1.3\pi$ and $\alpha=0.7\pi, \beta=1.65\pi$ in Fig.~\ref{fig:StructureFactors}(f) and (g), respectively. Since the SSFs are peaked at $\tilde{\Gamma}$ point of the first BZ, so both phases have ferromagnetic orders and they are denoted with FM-A and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}. We note that there are two special points with $J=K=0$ and $\Gamma=\pm1$ in the two FM phases, which are located at the phase boundary in the classical phase diagram~\cite{PhysRevB.92.165108}. Thus, it is worthy to discuss the properties of the pure $\Gamma$ models in details, and we perform the numerical simulations by using the ``basin-hopping" global optimization and classical Monte Carlo methods. For $\Gamma=+1$, apart from the FM GS with the spin orientation lying in the lattice plane, we also found disordered states having the same energy as the FM state. For $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, other long-range ordered states which are energetically degenerate with the FM state also appear (see Appendix~\ref{apx:DegeneratedStates} for details). However, for the quantum model, quantum flucations select the FM ordered states as the GS out of the degenerate manifolds of classical states according to our ED calculations. This selection of states among the degenerate classical ground states is the so the called order-by-disorder mechanism, which has previously been applied in a number of insulating magnets, especially in cases where frustration leads to a degenerate manifold of classical ground state configurations that is broken by quantum fluctuations~\cite{JPSJ.54.4494,PhysRevLett.62.2056,PhysRevLett.88.067203,PhysRevB.81.214419,PhysRevLett.109.077204}.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/StructureFactors.pdf}
    \caption{\label{fig:StructureFactors}(Color online) SSF for different model paramters. The green dashed lines marks the first BZ corresponding to the triangular lattice. See Appendix~\ref{apx:SSF} for SSF profiles of other representative model parameters.}
\end{figure}

@@

Although we have basically determine the nature of each phase, there are still two problems should be explained: first, why there are phase transitions between the phases with the same type of classical orders, such as the phase transitions between FM phases or stripe phases, and why the FM and stripe phases of the HK model are the phase boundaries in the global phase diagram of $J$-$K$-$\Gamma$ model; second, what other important characteristics of the possible QSL phase in the phase diagram can be used to help us understand its properties more deeply. In the followings, we will address these problems.

\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{fig/ModulatedStripe.pdf}
    \caption{\label{fig:ModulatedStripe}(Color online) Illustration of the modulated stripe order. (a) The spin configuration obtained from basin-hopping optimization for a $12 \times 12$ cluster. (b) Classical spin structure factor corresponding to the spin configuration shown in (a). (c) The spin configuration obtained from classical Monte Carlo for a $24 \time 24$ cluster.}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/Probabilities.pdf}
    \caption{\label{fig:Proabilities}(Color online) Map of the probabilities of the cluster spin-coherent state given by Eq.~\eqref{eq:ClusterCoherentState} in varies exact cluster GS. The radial and polar coordinate gives the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig.~\ref{fig:ModelDefinition}(b). The green dashed lines and solid circles mark the ordered moment direction for the classical states, see main text for details.}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/Spectrum.pdf}
    \caption{\label{fig:Spectrum}(Color online) Spin excitation spectrum for $\alpha=0.05\pi,\beta=0.1\pi$. $A(\bm{k}, \omega)$ is draw along the path $\tilde{M}-\tilde{\Gamma}-\tilde{M}-\tilde{\Gamma}$.}
\end{figure}

>>>>

Geometric frustration, which arises when the lattice geometry gives rise to constraints that not every exchange bond can be simultaneously minimized in energy, plays an important role in various kinds of magnetic systems. The nearest-neighbor (NN) antiferromagetic (AFM) Heisenberg model on the triangular lattice is a typical example, once two of the spins on an elementary triangle are antiparallel to satisfy their antiferromagnetic interaction, the third one can no longer point in a direction opposite to both other spins. In particular, the spin-1/2 case has attracted numerous interests and was extensively studied after the seminal prediction by Anderson of a ``quantum spin liquid" (QSL) where a strong quantum fluctuation prevents any long-range order down to the zero temperature~\cite{Anderson1973}, although it has been shown by later studies that the ground state (GS) have a classical magnetic order with each spin on a triangle pointing to 120$^\circ$ with respect to each other~\cite{PhysRevLett.99.127004,PhysRevLett.82.3899,PhysRevB.50.10048,PhysRevLett.60.2531}. When the second NN interactions are included which introduce further frustration, the system has a much richer phase diagram including the 120$^\circ$ N\'{e}el state, the stripe state and a QSL state~\cite{PhysRevB.91.014426,PhysRevB.92.041105,PhysRevB.92.140403,PhysRevB.96.165141,PhysRevB.93.144411,JPSJ.83.093707,PhysRevB.96.075116,PhysRevB.94.121111,PhysRevLett.123.207203}. All these studies have revealed that geometric frustated systems show quite different behavior from that of the non-frustated system.

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/ModelDefinition.pdf}
    \caption{\label{fig:ModelDefinition}(Color online) (a) Top view of the triangular lattice of the edge-sharing octahedron. (b) The orientation of the cubic $x$, $y$, $z$ axes with respect to the octahedron. The spin operators $S^x$, $S^y$ and $S^z$ are defined with respect to this reference frame. (c) Three types of the NN bonds on the triangular lattice, namely $\gamma=x, y, z$ colored red, green and blue, respectively. The different colors of the lattice sites label the four sublattices realizing the four sublattice transformation ( see main text for details).}
\end{figure}
In fact, magnetic ions located at the center of edge-sharing octahedra can not only form the honeycomb lattice but also the triangular lattice (see Fig.~\ref{fig:ModelDefinition}(a)), so the Kitaev and $\Gamma$ terms can naturally be generalized to the triangular lattice~\cite{PhysRevB.89.014414,PhysRevB.93.104417}. On the experimental side, studies of several classes of rare-earth compounds have recently shown that the quantum spin model on the triangular lattice can be formed by $4f$ moments. In particular, due to their possible Kramers doublets and spin-orbital coupling, the $4f$ electrons can be treated as $S_{eff}=1/2$ at low temperatures, and the spin-orbit entanglement can induce direction-dependent exchanges, such as the $K$ and $\Gamma$ terms. A typical example is YbMgGaO$_{4}$~\cite{srep16419,PhysRevLett.115.167203} and YbZnGaO$_{4}$~\cite{PhysRevLett.120.087201}, in which the Yb$^{3+}$ ions form a triangular layer and are surrounded by O$^{2-}$ which construct edge sharing octahedra. More recently, an alternative family of compounds AReCh$_2$ (A=alkali, Re=rare-earth, Ch=O, S, Se) with perfect triangular lattices of rare-earth ions have been synthesized and explored. The magnetic susceptibilty and heat capacity data suggest no long-range magnetic order or spin freezing down to the lowest measurement temperature, which implies their candidacy for QSL state~\cite{acsmaterialslett.9b00464,PhysRevMaterials.3.114413,PhysRevB.100.241116,Liu_2018,PhysRevB.99.180401,PhysRevB.100.224417,PhysRevB.100.144432}. These triangluar magnets of rare-earth ions provide suitable platforms to study the interplay of geometric frustation and exchange frustration induced by spin-orbit coupling.

The phase diagram of the HK model ($\Gamma=0$) on the triangular lattice has been studied by means of Luttinger-Tisza minimization together with classical Monte Carlo simulation~\cite{PhysRevB.93.104417}, exact diagonalization (ED)~\cite{PhysRevB.91.155135,KaiLi2015}, and density matrix renormalization group~\cite{JPSJ.85.114710,PhysRevX.9.021017}. All these methods give consistent results about four magnetically ordered phases: two collinear patterns of FM and stripe types, and two noncollinear patterns of 120$^\circ$ N\'{e}el and noncoplanar spiral types. Note that the distortions of the 120$^\circ$ N\'{e}el order, when the model deviates from the AFM Heisenberg limit ($K=0$, $J>0$), were also called the $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417,PhysRevB.91.155135,JPSJ.85.114710}. However, the nature of the phase around the antiferromagnetic Kitaev point is still under debate. The Luttinger-Tisza minimization method suggested it to be a $Z_{2}$ vortex crystal~\cite{PhysRevB.93.104417}, the Schwinger-fermion mean-field theory proposed it to be a QSL~\cite{KaiLi2015}, while the density matrix renormalization group calculations suggested it to be a nematic phase~\cite{PhysRevB.91.155135,JPSJ.85.114710} or a stripe phase~\cite{PhysRevX.9.021017}. When the symmetric off-diagonal $\Gamma$ interaction is included, a classical analysis reveals that the stripe and ferromagnetic phases dominate the $J$-$K$-$\Gamma$ phase diagram, in addition to small regions of 120$^\circ$ N\'{e}el, $Z_{2}$ vortex crystal and nematic phases~\cite{PhysRevB.92.165108}. However, the studies on the effects of quantum fluctuations on the global $J$-$K$-$\Gamma$ phase diagram are scarce. In particular, since no exact solution has been reported so far for the pure spin-$1/2$ Kitaev and $\Gamma$ models on the triangular lattice, it also remains conceptually interesting to investigate whether QSL states could exist as possible GSs due to quantum fluctuations introduced by these exchange-frustrated interactions.

In this paper, we study the global phase diagram and the phase transitions of the triangular lattice $J$-$K$-$\Gamma$ model using a combination of ED and classical analyses. We find that the ED results are basically consistent with the classical analyses such as the classical Monte Carlo simulations. In the HK limit ($\Gamma=0$), there are five classical phases: one FM, two stripe, one $120^{\circ}$ N\'{e}el and its dual phases. For the pure AFM Kitaev model, although the system has highly degenerate classical GSs composed of the stripe and nematic states, the order-by-disorder mechanism caused by quantum fluctuations makes the system select the stripe state to be the GS. When the $\Gamma$ term is included, we find five new phases: two FM, one stripe, one modulated stripe and one possible QSL phases. With the aid of classical analysis, we determine the spin directions for each magnetically ordered phase and explain that why there are phase transitions between the phases with the same type of classical orders. On the other hand, we find that the order-by-disorder mechanism makes the GSs of the pure $\Gamma$ models have FM orders, although the classical analyses suggest that the GSs are highly degenerate. For the possible QSL phase, based on the investigation of the spin excitation spectrum, we find that the GS is probably a gapped $Z_{2}$ QSL.

%The rest of the paper is organized as follows: In Sec.~\ref{sec:Model} we introduce the $J$-$K$-$\Gamma$ model as well as the four-sublattice-transformation that can be applied to the HK limit. The ED and classical Monte Carlo methods are introduced in Sec.~\ref{sec:Methods}. Section~\ref{sec:Results} gives the main results of this paper.

\section{Model and Methods}

\subsection{\label{sec:Model}Model}

@@

In the followings, for convenience, we fix the energy scale with $\sqrt{J^2 + K^2 + \Gamma^2}=1$ and parametrize the exchange parameters using spherical angles $\alpha$ and $\beta$
\begin{equation}
    J = \sin\alpha \sin\beta, \quad
    K = \sin\alpha \cos\beta, \quad
    \Gamma = \cos\alpha
    \label{eq:Parameters}
\end{equation}
where $\alpha \in [0, \pi]$ and $\beta \in [0, 2\pi]$ to cover the global parameter space.

In the HK limit ($\Gamma=0$), the model~\eqref{eq:Hamiltonian} admits an exact duality transformation, i.e., the so-called four-sublattice-transformation (FST)~\cite{PhysRevB.89.014414}. The FST is a spin rotation transformation which divides the triangluar lattice into four sublattices (see Fig.~\ref{fig:ModelDefinition}(c)) and performs the following rotations of the spins on the four sublattices to map the spin $\bm{S}_{i}$ to $\bm{S}_{i}^{\prime}$,
\begin{align*}
    & \bm{S}_{0}^{\prime} = \bm{S}_{0}& \quad \text{for sublattice 0}, \\
    & \bm{S}_{1}^{\prime} = (S_1^x, -S_1^y, -S_1^z)& \quad \text{for sublattice 1}, \\
    & \bm{S}_{2}^{\prime} = (-S_2^x, S_2^y, -S_2^z)& \quad \text{for sublattice 2}, \\
    & \bm{S}_{3}^{\prime} = (-S_3^x, -S_3^y, S_3^z)& \quad \text{for sublattice 3}.
\end{align*}
This corresponds to a $\pi$ rotation around $x$, $y$, and $z$ axis for the spin operators on the sublattices $1$, $2$, and $3$, respectively. The resulting Hamiltonian $H^{\prime}(\bm{S}^{\prime})$ has the same form as the original Hamiltonian albeit with different model parameters $J^{\prime} = -J$ and $K^{\prime} = 2J + K$. For the spherical angles defined in Eq.~\eqref{eq:Parameters}, the mapping takes the form
\begin{align}
    \tan\beta^{\prime} = -\sin\beta / (2\sin\beta + \cos\beta).
    \label{eq:FST}
\end{align}
This special property of the model can help us to identify some exotic magnetically ordered phases from the well established simple counterparts.

%\section{\label{sec:Methods}Methods}

\subsection{\label{subsec:MethodED}Exact Diagonalization method}

@@

To further determine the magnetic configurations of the magnetically ordered phases, we employ a method by studying the projections of the exact GSs of the finite cluster to the classical states~\cite{PhysRevB.94.064435}. The basic idea of this method is to measure the probabilities of the cluster spin coherent states in the exact cluster GS with varying moment directions. The cluster spin coherent state is a direct product of spin-1/2 coherent states on each site $i$, i.e.,
\begin{align}
    | \Psi \rangle = \bigotimes_{i=1}^{N} | \theta_{i}, \phi_{i} \rangle,
    \label{eq:ClusterCoherentState}
\end{align}
where the spin-1/2 coherent state
\begin{align}
    | \theta, \phi \rangle = \mathcal{R}_{z}(\phi) \mathcal{R}_{y}(\theta) | \uparrow \rangle = e^{-i \phi S^z} e^{-i \theta S^y} | \uparrow \rangle
    \label{eq:Spin-1/2CoherentState}
\end{align}
is fully polarized state along the $(\theta, \phi)$ direction. Here the cubic axes are used (see Fig.~\ref{fig:ModelDefinition}(b)), $\theta$ and $\phi$ are the conventional spherical angles. By calculating the overlap between the exact cluster GS and cluster spin conherent states, $P = | \langle \Psi | GS \rangle |^2$, and maximizing its value with respect to $\theta$'s and $\phi$'s, we can then identify the classical spin pattern that best fits the exact quantum GS.

Since one of the key characteristics of QSL is the fractional excitation, which can lead to a continuous spectrum, so we study the dynamic structure factor (DSF) $A(\bm{k}, \omega)$ to search for the possible QSLs. $A(\bm{k}, \omega)$ is given by
\begin{align}
    & A(\bm{k}, \omega) = -\frac{1}{\pi} \text{Im} \mathcal{S}(\bm{k}, \omega), \label{eq:Akomega} \\
    & \mathcal{S}(\bm{k}, \omega) = \frac{1}{N} \sum_{ij} \mathcal{S}_{ij}(\omega) e^{i \bm{k} \cdot (\bm{R}_i - \bm{R}_j)}, \\
    & \mathcal{S}_{ij}(\omega) = \langle \Omega | S_i^{+} \frac{1}{\omega + i0^{+} - H + E_0} S_j^{-} | \Omega \rangle, \label{eq:GreenFunction}
\end{align}
where $E_0$ is the GS energy.

\subsection{\label{subsec:MethodMC}Classical Monte Carlo method}

@@

From the magnetic configuration of GS, we compute the SSF given by
\begin{align}
    \mathcal{S}_{\bm{k}} = \frac{1}{N} \sum_{ij} \left \langle \bm{S}_i \cdot \bm{S}_j \right \rangle e^{i \bm{k} \cdot (\bm{r}_i-\bm{r}_j)},
\end{align}
which is a key characteristic to identify magnetic phases.

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.95\textwidth]{fig/QuantumGlobalPhaseDiagram.pdf}
    \caption{\label{fig:QuantumPhaseDiagram}(Color online) Global phase diagram of the triangular lattice $J$-$K$-$\Gamma$ model. The angle $\alpha$ and $\beta$ denote the radial and azimuthal angles, respectively. There are in total ten phases including three FM phases denoted as FM-A, FM-B and FM-C, three stripe phases designated as Stripe-A, Stripe-B and Stripe-C, a modulated stripe phase, a 120$^\circ$ N\'{e}el phase, a dual N\'{e}el phase and a possible QSL phase. Phase boundaries are determined by the singularities of $-\partial^2E_0/\partial\alpha^2$ and $-\partial^2E_0/\partial\beta^2$ from ED calculations except for that depicted by the dashed line between the modulated stripe and stripe-B phases given by the classical analyses.}
\end{figure*}

@@

For the other two phases with large areas and mainly located in the $J<0$ region of the phase diagram, we show the SSFs of two representative points with $\alpha=0.3\pi, \beta=1.3\pi$ and $\alpha=0.7\pi, \beta=1.65\pi$ in Fig.~\ref{fig:StructureFactors}(f) and (g), respectively. Since the SSFs are peaked at $\tilde{\Gamma}$ point of the first BZ, so both phases have ferromagnetic orders and they are denoted with FM-A and FM-C in Fig.~\ref{fig:QuantumPhaseDiagram}. We note that there are two special points with $\Gamma=\pm1$ ($J=K=0$) in the two FM phases, which are located at the phase boundary in the classical phase diagram~\cite{PhysRevB.92.165108}. Thus, it is worthy to discuss the properties of the pure $\Gamma$ models in details, and we perform the numerical simulations by using the ``basin-hopping" global optimization and classical Monte Carlo methods. For $\Gamma=+1$, apart from the FM GS with the spin orientation lying in the lattice plane, we also found disordered states having the same energy as the FM state. For $\Gamma=-1$, in addition to the FM order perpendicular to the lattice plane, other long-range ordered states which are energetically degenerate with the FM state also appear (see Appendix~\ref{apx:DegeneratedStates} for details). However, for the quantum model, quantum flucations select the FM ordered states as the GS out of the degenerate manifolds of classical states according to our ED calculations. This selection of states among the degenerate classical ground states is the so the called order-by-disorder mechanism, which has previously been applied in a number of insulating magnets, especially in cases where frustration leads to a degenerate manifold of classical ground state configurations that is broken by quantum fluctuations~\cite{JPSJ.54.4494,PhysRevLett.62.2056,PhysRevLett.88.067203,PhysRevB.81.214419,PhysRevLett.109.077204}.
\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/StructureFactors.pdf}
    \caption{\label{fig:StructureFactors}(Color online) (a)-(h) Representative SSFs from the ED calculations for different interaction parameters. The green dashed lines marks the first BZ corresponding to the triangular lattice. (i) Characteristic wave vectors for the FM and stipe phases. See Appendix~\ref{apx:SSF} for the SSFs of the 120$^\circ$ N\'{e}el phase, dual N\'{e}el phase and pure $\Gamma$ models.}
\end{figure}

@@

So far, we have basically determine the nature of each phase, but there are still two problems should be explained: first, why there are phase transitions between the phases with the same type of classical orders, such as the phase transitions between FM phases or stripe phases, and why the FM and stripe phases of the HK model are the phase boundaries in the global phase diagram of $J$-$K$-$\Gamma$ model; second, what other important characteristics of the possible QSL phase in the phase diagram can be used to help us understand its properties more deeply. In the followings, we will address these problems.

\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{fig/ModulatedStripe.pdf}
    \caption{\label{fig:ModulatedStripe}(Color online) (a) Spin configuration obtained from basin-hopping optimization for a $12 \times 12$ cluster. (b) SSF corresponding to the spin configuration shown in (a). (c) Spin configuration obtained from the classical Monte Carlo calculations for a $24 \times 24$ cluster.}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/Probabilities.pdf}
    \caption{\label{fig:Proabilities}(Color online) Map of the probabilities of the cluster spin coherent state given by Eq.~\eqref{eq:ClusterCoherentState} in exact cluster GS for (a) FM-A, (b) FM-C, (c) stripe-A and (d) stripe-B phases. The radial and polar coordinate gives the angles $\theta$ and $\phi$, which are spherical angles with respect to the reference frame shown in Fig.~\ref{fig:ModelDefinition}(b). The green dashed lines and solid circles mark the ordered moment directions for the classical states. Note that the GSs are six-fold degenerate for the stripe-A and stripe-B phase, and two-fold degenerate for the FM-C phase, so the total probabilities for all of these phases are approximate to $1$. }
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{fig/Spectrum.pdf}
    \caption{\label{fig:Spectrum}(Color online) DSF $A(\bm{k}, \omega)$ for $\alpha=0.05\pi,\beta=0.1\pi$ in the QSL phase. The path $\tilde{M}-\tilde{\Gamma}-\tilde{M}-\tilde{\Gamma}$ is shown in Fig.~\ref{fig:StructureFactors}(i).}
\end{figure}
